Effect of quality-adjusted production function inputs

### 2015-05-06 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now includes graphs of fits to historical data.

@@

>>>>

<<Fitted_Data>>=
extract_fitted_comparison <- function(mod, id){
  df <- mod$data[ , c("Year", "iGDP", "Country")]
  # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
  df$fitted <- yhat(mod)[c(1:length(df$Year))]
  # Parse the id to find out whether this is quality-adjusted data
  id_list <- strsplit(id, split = "[.]")[[1]]
  if (id_list[[2]] == "unadj"){
    df$adjusted <- "Unadjusted"
  } else if (id_list[[2]] == "adj"){
    df$adjusted <- "Quality-adjusted"
  } else {
    stop("Unknown adjustment.")
  }
  if (id_list[[3]] == "noE"){
    df$energy <- "Without energy"
  } else if (id_list[[3]] == "withE"){
    df$energy <- "With energy"
  } else {
    stop("Unknown energy.")
  }
  df$model <- id_list[[4]]    
  return(df)
}
fitted_data <- leaf_apply(models, extract_fitted_comparison, class=c("CDEmodel", "cesEst", "LINEXmodel"))
fitted_data <- do.call(rbind, fitted_data)
# Melt fitted_data so it can be used for plotting
# Relevel factors before plotting
fitted_data$Country <- relevelFactor(as.factor(fitted_data$Country), c("PT", "UK"))
fitted_data$adjusted <- relevelFactor(as.factor(fitted_data$adjusted), c("Unadjusted", "Quality-adjusted"))
fitted_data$energy <- relevelFactor(as.factor(fitted_data$energy), c("Without energy", "With Energy"))
@

@@

%++++++++++++++++++++++++++++++
\subsection{Fits to historical data} 
\label{sec:fits_to_historical_data}
%++++++++++++++++++++++++++++++

This section shows graphs of fits to historical data.

<<Fitted Graph>>=
fittedGraph <- function(data){
  ggplot() +
    geom_line(data=filter(data, energy=="Without energy"), mapping=aes(x=Year, y=iGDP)) +
    geom_line(data=data, mapping=aes(x=Year, y=fitted, linetype=energy)) +
    scale_linetype_manual(values=c(2,3), name="") +
    facet_grid(Country ~ adjusted) +
    xy_theme()
}
@

<<Graphs CD, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Cobb-Douglas models. Solid line is historical GDP.">>=
fittedGraph(filter(fitted_data, model=="CD"))
@

<<Graphs CESkle, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($kl$)$e$ nesting. Solid line is historical GDP.">>=
fittedGraph(filter(fitted_data, model=="CESkle" | model=="CESkl"))
@

<<Graphs CESlek, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($le$)$k$ nesting. Solid line is historical GDP.">>=
fittedGraph(filter(fitted_data, model=="CESlek" | model=="CESkl"))
@

<<Graphs CESekl, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="CES models with ($ek$)$l$ nesting. Solid line is historical GDP.">>=
fittedGraph(filter(fitted_data, model=="CESekl" | model=="CESkl"))
@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Analysis}
\label{sec:analysis}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
